---
title: "p8105_hw6_yl4362"
output: github_document
---

```{r setup, message = FALSE}
library(tidyverse)
library(modelr)
```

## Problem 1

```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv") %>%
  mutate(city_state = str_c(city, state, sep = ", "),
         victim_age = as.numeric(victim_age),
         resolution = case_when(
           disposition == "Closed without arrest" ~ 0,
           disposition == "Open/No arrest" ~0,
           disposition == "Closed by arrest" ~1
         )) %>%
  filter(city_state != "Tulsa, AL",
         victim_race %in% c("White", "Black")) %>%
  select(city_state, resolution, victim_age, victim_sex, victim_race)

homicide_baltimore = 
  homicide_df %>%
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = homicide_baltimore, 
    family = binomial()) %>%
  broom::tidy() %>%
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
    ) %>%
  select(term, OR, starts_with("CI")) %>%
  knitr::kable(digits = 3)

models_results_df = 
  homicide_df %>%
  nest(data = -city_state) %>%
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = .x, 
    family = binomial())),
    results = map(models, broom::tidy)
  ) %>%
  select(city_state, results) %>%
  unnest(results) %>%
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
    ) %>%
  select(city_state, term, OR, starts_with("CI"))

models_results_df %>%
  filter(term == "victim_sexMale") %>%
  mutate(city_state = fct_reorder(city_state, OR)) %>%
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Problem 2

```{r}
birthweight_df = 
  read_csv("./data/birthweight.csv") %>%
  mutate(
    babysex = case_when(
      babysex == 1 ~ "male",
      babysex == 2 ~ "female"
    )
  ) %>%
  drop_na(blength, gaweeks, bhead, babysex)

m1 =
  lm(bwt ~ momage + wtgain, data = birthweight_df)

m1 %>%
  broom::tidy() %>%
  select(term, estimate, p.value)

birthweight_df %>%
  modelr::add_residuals(m1) %>%
  modelr::add_predictions(m1) %>%
  ggplot(aes(x = momage, y = resid)) + 
  geom_point() +
  geom_line(aes(y = pred), color = "red")
```
In the `m1` model, I used mom's gained weight and mom's age as predictors.

``` {r}
cv_df =
  crossv_mc(birthweight_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(
    m1_mod = map(train, ~lm(bwt ~ momage + wtgain, data = .x)),
    m2_mod = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    m3_mod = map(train, ~lm(bwt ~ bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = .x))
    ) %>% 
  mutate(
    rmse_m1 = map2_dbl(m1_mod, test, ~rmse(model = .x, data = .y)),
    rmse_m2 = map2_dbl(m2_mod, test, ~rmse(model = .x, data = .y)),
    rmse_m3 = map2_dbl(m3_mod, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```
The RMSEs are suggestive that `m3` model works best.

## Problem 3

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm")
```

### log_(beta0*beta1)
```{r}
log_beta =
  weather_df %>%
  modelr::bootstrap(n = 5000) %>%
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy)) %>%
  select(-strap, -models) %>%
  unnest(results) %>%
  select(.id, term, estimate) %>%
  pivot_wider(
    names_from = term,
    values_from = estimate,
    values_fn = list
  ) %>%
  mutate(
    intercept = as.numeric(`(Intercept)`),
    tmin = as.numeric(tmin),
    log_beta01 = log(intercept * tmin)) %>%
  select(log_beta01)

log_beta_distribution =
  log_beta %>%
  ggplot(aes(x = log_beta01)) + geom_density()

log_beta_distribution

log_beta %>%
  summarize(ci_lower = quantile(log_beta01, 0.025), 
    ci_upper = quantile(log_beta01, 0.975)) %>%
  knitr::kable(digits = 3)
```
From the log_beta_distribution plot, we can see most of the values of log(beta0*beta1) are between 1.95 and 2.05 The 95% CI for r_squared is (1.964, 2.058).


### r_squared
``` {r}
r_2 = 
  weather_df %>%
  modelr::bootstrap(n = 5000) %>%
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::glance)) %>%
  select(-strap, -models) %>%
  unnest(results) %>%
  select(r.squared) 

r_2_distribution =
  r_2 %>%
  ggplot(aes(x = r.squared)) + geom_density()

r_2_distribution

r_2 %>%
  summarize(ci_lower = quantile(r.squared, 0.025), 
    ci_upper = quantile(r.squared, 0.975)) %>%
  knitr::kable(digits = 3)
```
From the r_2_distribution plot, we can see most of the values of r_squared are between 0.90 and 0.92. The 95% CI for r_squared is (0.894, 0.927).

